---
title: "ETL in R"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
---


# Deliverable 1
```{r}
# Set URLs for data sets
states_url <- "https://github.com/mattstern2/BUA-301-Term-Project-Fall-2024/raw/main/States.csv"
swift_transactions_url <- "https://github.com/mattstern2/BUA-301-Term-Project-Fall-2024/raw/main/Swift_Transactions.csv"

```


# Deliverable 2 Question Responses


# Deliverable 2 Code
```{r}

```


# Deliverable 3a Code
```{r}

```


# Deliverable 3b Code
```{r}

```


# Deliverable 3c Code
```{r}

```


# Deliverable 4 Code
```{r}

```


# Deliverable 5a Question Response


# Deliverable 5a Code
```{r}

```


# Deliverable 5b Question Response


# Deliverable 5b Code
```{r}

```


# Deliverable 5c Question Response


# Deliverable 5c Code
```{r}

```


# Deliverable 5d Question Response


# Deliverable 5d Code
```{r}

```


# Deliverable 6a Question Response


# Deliverable 6a
```{r}

```


# Deliverable 6b
```{r}

```


# Deliverable 6c
```{r}

```


# Deliverable 6d
```{r}

```


# Deliverable 6e
```{r}

```


# Deliverable 6f
```{r}

```


# Deliverable 6g Question Response


# Deliverable 6g
```{r}

```


# Deliverable 6h Question Response


# Deliverable 6h
```{r}

```


